Title Goes Here

### 2023-11-01 paper/main.tex
edits

\newcommand{\system}{\textsc{SystemName}\xspace}

@@

@@

[TODO: any commentary about the actual python script?]

@@

Our python script for actually performing the test consumes a stream of fixed-length bit vectors.
(In practice, this is a CSV. Annotation of which columns are available in the real and ideal worlds is provided in the header.)
[Does our tool strictly need the vectors to be fixed width? Could someone do this kind of test on a system with branching control flow?]
To facilitate analysis of the tool, we implemented a choreographic programming language, CHO,
with surrounding tooling to support large batches of parallel evaluations of a single program and piping of the generated data.
The design of CHO is driven by the contextual assumptions of MPC security.
[Do we want a BNF? Semantics?]
In addition to bit-level computations and transmission of single bits between arbitrary parties,
each party has its own read-only tape for secret inputs and random bits
(CHO is also a probabilistic language),
and its own tape for output bits.
CHO supports macros, but they are extremely limited.
Finally, CHO supports 1-of-N oblivious transfer as a primitive operation.
This allows us to test (correct and incorrect) implementations of the classic GMW protocol.

@@

The goal of this work is a tool that can detect mistakes in MPC protocols.
Such a tools is only useful if there if new protocols and implementations are being written.
Therefore, while it is critical to demonstrate that our tool can detect errors manually edite into known-secure protocols,
we \textit{also} need to show that the tool can detect a lack of security in entirely novel and maximally diverse protocols.
We attempt to show this by randomly generating hundreds [can we say thousands?] of protocols and testing them with different test parameters.

The probability that a randomly generated protocol will be MPC secure is not completely negligible.
As an easy example, if no communicated values ever depend on secret inputs, then the protocol meets the definition of security!
(Never mind that such a protocol is useless; \textit{none} of the protocols we generated are \textit{useful}.)
That said, for reasonable generator settings we find that \textit{very few} generated protocols
continue to appear secure as we increase the power of the test.

>>>>

\newcommand{\system}{\textsc{\textbf{.}CHO}\xspace}

@@

\subsection{Implementation}

Our python script for actually performing the test consumes a stream of fixed-length bit vectors as a CSV.
Annotation of which columns are available in the real and ideal worlds is provided in the header.
The CSV is parsed and broken up as needed as a \texttt{pandas} dataframe.
The individulal ML models are instances of \texttt{sklearn.tree.DecisionTreeClassifier},
and they're trained in parallel with \texttt{joblib.Parallel}.
The D-Tree scores are inflated by $+1 \cdot 10^{-10}$ to avoid division-by-zero in the score-ratio,
and the score distributions are compared by \texttt{scipy.stats.wilcoxon}.

TODO: link to github or other archive?

@@

@@

To facilitate analysis of the tool, we implemented a choreographic programming language, \system,
with surrounding tooling to support large batches of parallel evaluations of a single program and piping of the generated data.
(In particular, the semantics are polymorphic within the Haskell type-class \texttt{Data.Bits.FiniteBits},
\eg sixty four evaluations can run in a single thread by applying the semantics to the \texttt{Word64} type.)
The design of \system is driven by the contextual assumptions of MPC security.
In addition to bit-level computations and transmission of single bits between arbitrary parties,
each party has its own read-only tapes for secret inputs and randomness,
and its own tape for output bits.
\system supports macros, but they are extremely limited.
Finally, \system supports 1-of-N oblivious transfer as a primitive operation.
This allows us to test (correct and incorrect) implementations of the classic GMW protocol.

TODO: refer to an example figure and/or an appendix.

@@

The goal of this work is a tool that can detect mistakes in MPC protocols.
Such a tools is only useful if there if new protocols and implementations are being written.
Therefore, while it is critical to demonstrate that our tool can detect errors manually edited into known-secure protocols,
we \textit{also} need to show that the tool can detect a lack of security in entirely novel and maximally diverse protocols.
We attempt to show this by randomly generating hundreds [can we say thousands?] of protocols and testing them with different test parameters.

The probability that a randomly generated protocol will be MPC secure is not completely negligible.
In particular, some generator settings will be biased toward vacuous protocols in which nothing is communicated
or vacuously secure protocols in which the honest secrets are fully revealed by the ideal functionality.
(Never mind that such protocols are useless; none of the protocols generated in this experiment are \textit{useful}.)
That said, for reasonable generator settings we find that very few generated protocols
continue to appear secure as we increase the power of the test.
